---
title: "Probability Distributions"
author: "Easy Data Science"
date: "6/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(datasets)
library(tidyr)
library(ggthemes)
library(moments)
library(lubridate)
library(data.world)
```


## Distribution

 
In your website, 1 in every 5 people spend more than 30 seconds. If you pick random 10 people, what is the probability that 2 of them have spent more than 30 seconds.
- less than or equal 3


```{r}
p_s30<-1/5
r_s<-10
v<-2
dbinom(v,r_s,p_s30)

v<-c(0,1,2,3)
sum(dbinom(v,r_s,p_s30))

ps<-c(0.25)
pbinom(ps, r_s, p_s30)

rbinom(2,10,0.2)

dpois()
dnorm()
```


What is the probability that in 1 day, 5 sales will be executed, when mean sales per day is 4?

```{r}
dpois(5,4)
sum(dpois(c(0:5),4))

c(0:5) %>% 
  dpois(4) %>% 
  sum()

rpois(5, 4)
```

What is the probability that a randomly selected person spends more than 50 seconds, given mean is 45 seconds and sd is 10?


```{r}
dnorm(50, 45, 10)

1-sum(dnorm(0:50, 45, 10))

```

## Confidence Interval

```{r}
s.size<- 25
s.mean<- 300
s.sd<- 18.5
#confidence interval of 95%

m <- qt(0.975,df=s.size-1)*s.sd/sqrt(s.size)

l.m<-s.mean-m
h.m<-s.mean+m

```



```{r}
s.size1 <- 15
s.mean1 <- 310 
s.sd1 <- 18.5

s.size2 <- 15
s.mean2 <- 300
s.sd2 <- 16.4

pool.var = ((s.size1-1)*s.sd1^2 + (s.size2-1)*s.sd2^2) / (s.size1+s.size2-2)

m <- qt(0.975,df=s.size1+s.size2-2)*sqrt(pool.var/s.size1 + pool.var/s.size1)

ldm <- (s.mean1-s.mean2) - m
udm <- (s.mean1-s.mean2) + m


```



```{r}
s.size <- 100
s.prop <- .56

m <- qnorm(0.975)*sqrt(s.prop*(1-s.prop)/s.size)

lp<-s.prop-m
hp<-s.prop+m

```


```{r}
s.size1 <- 100
s.prop1 <- .62

s.size2 <- 100
s.prop2 <- .46


m <- qnorm(0.975)*sqrt(s.prop1*(1-s.prop1)/s.size1 + s.prop2*(1-s.prop2)/s.size2)

lpd<-s.prop1-s.prop2-m
upd<-s.prop1-s.prop2+m

```
